Ecological validity of detecting data fabrication in experimental studies.

### 2016-05-23 submission/manuscript.Rmd
Correct an error from the preregistration.
Update filepaths

$\tilde{s}^2_j\sim\Bigg[\frac{\chi^2_{N_j-1}s^2_j}{N_j-1}\Bigg]/MS_w$

@@

### Results.
```{r prep data study 1, echo = FALSE}
options(digits = 20)
# Compute the summary statistics for Many Labs
source('../functions/compute_summary_anch_ml.R')
# Process the collected, fabricated data
source('../functions/process_qualtrics_anch_01.R')

# Read the data
ml <- read.csv('../data/study_01/ml_summary_stats.csv', stringsAsFactors = FALSE)
qualtrics <- read.csv('../data/study_01/qualtrics_processed.csv', stringsAsFactors = FALSE)
ml$stat_know <- NA
ml$spss <- NA
ml$rcran <- NA
ml$stata <- NA
ml$sas <- NA
ml$matlab <- NA
ml$python <- NA
ml$other <- NA
ml$nopro <- NA
ml$noanch <- NA
ml$rng <- NA
ml$full <- NA
ml$tries <- NA
ml$descr <- NA
ml$bonus <- NA
ml$type <- 'ml'
qualtrics$type <- 'qualtrics'

@@

```{r compile results for detecting data fabrication, echo = FALSE}
# conduct the analyses iteratively
for (pp in unique(dat$referrer))
{
  # Loop through each study to compute the ANOVA results
  for (j in 1:4)
  {
    study_nr <- j    
    indexor <- dat$referrer == pp & dat$study == study_nr

>>>>

$\tilde{s}^2_j\sim\Bigg[\frac{\chi^2_{N_j-1}}{N_j-1}\Bigg]/MS_w$

@@

### Results.
```{r prep data study 1, echo = FALSE}
options(digits = 20)
# Compute the summary statistics for Many Labs
# source('../functions/compute_summary_anch_ml.R')
source('functions/compute_summary_anch_ml.R')
# Process the collected, fabricated data
# source('../functions/process_qualtrics_anch_01.R')
source('functions/process_qualtrics_anch_01.R')

# Read the data
# ml <- read.csv('../data/study_01/ml_summary_stats.csv', stringsAsFactors = FALSE)
# qualtrics <- read.csv('../data/study_01/qualtrics_processed.csv', stringsAsFactors = FALSE)
ml <- read.csv('data/study_01/ml_summary_stats.csv', stringsAsFactors = FALSE)
qualtrics <- read.csv('data/study_01/qualtrics_processed.csv', stringsAsFactors = FALSE)
ml$stat_know <- NA
ml$spss <- NA
ml$rcran <- NA
ml$stata <- NA
ml$sas <- NA
ml$matlab <- NA
ml$python <- NA
ml$other <- NA
ml$nopro <- NA
ml$noanch <- NA
ml$rng <- NA
ml$full <- NA
ml$tries <- NA
ml$descr <- NA
ml$bonus <- NA
ml$type <- 'ml'
qualtrics$type <- 'qualtrics'

@@

```{r compile results for detecting data fabrication, echo = FALSE}
dat_summary_file <- 'data/study1_res.csv'

# conduct the analyses iteratively
for (pp in unique(dat$referrer))
{
  # Loop through each study to compute the ANOVA results
  for (j in 1:4)
  {
    indexor <- dat$referrer == pp & dat$study == j
